Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/design.tex
References

Figure~\ref{fig:range} shows several examples.

@@

For example, \cc{word=<uint8='"'; many int8 | 'a'..'z'; uint8='"'>} parses a quoted
lowercase word into an array.

@@

Nail also includes an \cc{optional} combinator, which attempts to recognise a value, but succeeds
without consuming input when it cannot recognise that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.

@@

Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.

% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, for example,
%   balanced parentheses could be parsed as follows: \cc{paren = < uint8 ="("; optional *paren
%     ;uint8=")">}

>>>>

@@

For example, \cc{<uint8='"'; many int8 | 'a'..'z'; uint8='"'>} parses a quoted
lowercase word into an array.

@@

\paragraph{Optional.}Nail also includes an \cc{optional} combinator, which attempts to recognise a value, but succeeds
without consuming input when it cannot recognise that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.

@@

\paragraph{References.}Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.

For example example,   balanced parentheses could be parsed as follows: \cc{paren = < uint8 ="("; optional *paren;uint8=")">}

% To support recursive structures, we include a reference combinator \cc{*}, which
%   is syntactically equivalent to directly including the parser, but in the internal model adds a
%   level of indirection to the value. This allows recursive structures to be parsed, f
